Recruiting Chapter

### 2020-10-28 manuscript.Rmd
draft changes

@@

@@

>>>>

Figure \@ref(fig:villanova-religion) shows the ego network of Villanova University, with religious affiliation

Figure \@ref(fig:emory-region) shows the ego network of Emory University, with geographic region

Figure \@ref(fig:rank-cluster1) shows the academic reputation of private high schools visited by selected colleges universities in cluster 1

Figure \@ref(fig:race-cluster4) shows the racial composition of visited private high schools, selected colleges

@@

```{r}
df <- readRDS('./assets/tables/table_ego.RDS')
knitr::kable(
  df %>% select(ID,University,Cluster,Type,Rank,Characteristics,c1_lt10,c2_10to25,c3_25to50,`c4_50+`), row.names = F, # select(-ID, -Characteristics)
  caption = 'la la') %>% landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

@@

```{r villanova-religion, fig.align = 'center', echo = FALSE, out.width = "75%", fig.cap = "Ego network of Villanova University, with religious affiliation"}
knitr::include_graphics('assets/figures/villanova_religion.pdf')
```

```{r emory-region, fig.align = 'center', echo = FALSE, out.width = "75%", fig.cap = "Ego network of Emory University, with geographic region"}
knitr::include_graphics('assets/figures/emory_region.pdf')
```

```{r rank-cluster1, fig.align = 'center', echo = FALSE, out.width = "75%", fig.cap = "Academic rating of private high schools visited by selected colleges from cluster 1"}
knitr::include_graphics('assets/figures/rank_cluster1.pdf')
```

```{r race-cluster4, fig.align = 'center', echo = FALSE, out.width = "75%", fig.cap = "Racial composition of visited private high schools, selected colleges"}
knitr::include_graphics('assets/figures/race_cluster4.pdf')
```
